The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Reduce the size of Figures 5 and 6

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of correct \texttt{check-sat} answers (out of
    \num{30370517} total) within a time limit of \SI{2400}{s} on
    common benchmarks 2015--2018 of all logics in the \apptrack.}
  \label{fig:progress-all-app}
\end{figure}

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
  plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
  \vspace{-5ex}
  \caption{VBS in terms of number of unsat core reductions within a
    time limit of \SI{2400}{s} on common benchmarks 2016--2018 of all
    logics in the \ucoretrack.}
  \label{fig:progress-all-uc}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of correct \texttt{check-sat} answers (out
      of \num{30370517} total) within a time limit of \SI{2400}{s} on
      common benchmarks 2015--2018 of all logics in the \apptrack.}
    \label{fig:progress-all-app}
  \end{minipage}\hfill
  \begin{minipage}{0.47\textwidth}
    \centering
    \scalebox{.31}{\includegraphics{%
        plot/pdf/bar_plot-Virtual_Best_Solver_(VBS)_Unsat_Core_Track_2016-2018.pdf}}
    \vspace{-5ex}
    \caption{VBS in terms of number of unsat core reductions within a
      time limit of \SI{2400}{s} on common benchmarks 2016--2018 of
      all logics in the \ucoretrack.}
    \label{fig:progress-all-uc}
  \end{minipage}
\end{figure}
